\chapter{Call Volume Analysis}
\label{chap:call_vol_analysis}

\section{Validation of Historical Predictions}
% Content for validating historical predictions

\subsection{Predicted vs. Actual Call Volumes}
\todo{Del this enum when complete}
\todo{Is 2018 - 2023 the right date?}
\begin{enumerate}
    \item Overview of 2018 predictions for 2018-2023.
    \item Comparison of predicted total incidents vs. actual incidents.
    \item Breakdown by incident types (fire, EMS, hazardous materials, etc.).
\end{enumerate}

\subsection{Temporal Analysis}
\todo{Del this enum when complete}
\begin{enumerate}
    \item Predicted vs. actual incidents by time of day, day of week, month, etc.
    \item Identify any significant deviations and possible reasons.
\end{enumerate}

\subsection{Geospatial Comparison}
\todo{Del this enum when complete}
\begin{enumerate}
    \item Predicted vs. actual incident distribution maps.
    \item Analysis of high and low density areas.
    \item Discussion on how predictions matched real-world geographic trends.
\end{enumerate}

\section{Adjustments and Learnings}
\label{sec:adjustments_learnings}
% Content for Adjustments and Learnings

\subsection{Methodology Adjustments}
\todo{Del this enum when complete}
\begin{enumerate}
    \item Recommendations for improving prediction accuracy.
    \item Adjustments to be made in the future growth scenario models.
\end{enumerate}

\subsection{Study Insights}
\todo{Del this enum when complete}
\begin{enumerate}
    \item Key insights from the prediction vs. reality comparison.
    \item Identifying external factors influencing deviations (e.g., COVID-19, policy changes).
\end{enumerate}
