\chapter*{Glossary of Terms}
\addcontentsline{toc}{chapter}{Glossary of Terms}
\label{chap:glossary_of_terms}
% Content for glossary_of_terms
\begin{itemize}
    \item \textbf{AOR or Area of Responsibility}: a geographical area for which one fire station is primarily responsible. Generally, a station’s AOR corresponds approximately to the area in which it is closest by street distance or travel time. AORs are also sometimes called “first due areas” or “still alarm areas.”
    \item \textbf{Call File}: a digital file containing essential information about a collection of emergency incidents or calls, including each incident’s dispatch date/time, type, location, and other parameters.
    \item \textbf{Initial Response Time or IRT}: the elapsed time between the initial dispatch of an incident to the arrival of the first unit at the scene of the incident.
    \item \textbf{Model}: a digital representation of one potential way of organizing a fire agency, including station locations, staffing, apparatus placement, scheduling, dispatch policies, and other variables. Models typically include a “base model” (encoding the deployment and behavior of the current operational model) and the subsequent study items are altered from the base model to create new deployments.
    \item \textbf{Response Time}: the time between a unit’s notification (dispatch) of an incident and its arrival at the scene of the incident.
    \item \textbf{Scenario}: a digital collection of incidents designed to represent a possible future state of workload demand. Scenarios are typically generated by a statistical modeling process involving historical data, observed growth rates, and general and detailed development plans.
    \item \textbf{Simulation}: the process of performing detailed prediction of the behavior of a model or models, in response to a set of incidents (scenario or call file), at the level of individual staff members and apparatus on individual incidents.
    \item \textbf{Travel Time}: the time between a unit’s departure enroute to an incident and its arrival at the scene of the incident.
    \item \textbf{Turnout Time}: the time between a unit’s notification (dispatch) of an incident and its departure enroute to the incident.
\end{itemize}